### 2016-07-14 lineups.Rnw

\section{Introduction}

@@

ggplot(data=lus_ests_truth) +
  geom_bar(aes(x=model, fill=convergence), position="fill") + 
  facet_grid(.~true_model, labeller="label_both") +
  theme_bw() +
  theme(legend.position="bottom") + ylab("Ratio") +
  scale_fill_brewer("Convergence", palette="Set1") +
  xlab("Estimated Model")
@
\caption{\label{fig:convergence}Pattern of convergence. A total of 67.7\% of all lineup data converged in 5,000 iterations. The simplest model, $M_1$ has the highest rate of convergence. For models $M_2$ and $M_3$ data generated from the model converged at a higher rate than data generated from the other model.}
\end{figure}

@@

lus_summary_2 <- lus_spread %>% dplyr::group_by(part, lineupid, param_name) %>%
  dplyr::summarize(
    data_n = sum(true_model=="M2"),
    data_est = mean(M2[true_model=="M2"]),
    data_sd = sd(M2[true_model=="M2"], na.rm=TRUE),
    data_dist = data_est - max(M2[true_model=="M1"]),
    upper_qu = sum(data_est > M2[true_model=="M1"]) / (n()-1) 
)

@@

>>>>

<<setup, fig.keep='all', cache=FALSE, echo=FALSE, eval=TRUE, message=F, warning=F>>=
#rm(list=ls())
#wd <- getwd()
library(knitr)

options(replace.assign=TRUE,scipen=3, digits=2)

library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(gridExtra)
theme_set(theme_bw())
@
\section{Introduction}

@@

ggplot(data=lus_ests_truth) +
  geom_bar(aes(x=model, fill=convergence), position="fill", alpha = 0.6) + 
  facet_grid(.~true_model, labeller="label_both") +
  theme_bw() +
  theme(legend.position="bottom") + ylab("Ratio") +
  scale_fill_brewer("Convergence", palette="Set1") +
  xlab("Estimated Model")
@
\caption{\label{fig:convergence}Pattern of convergence. A total of 67.7\% of all lineup data converged in 5,000 iterations. The simplest model, $M_1$ has the highest rate of convergence. For models $M_2$ and $M_3$ data generated from the model converged at a higher rate than data generated from the other model.}
\end{figure}

@@

lus_summary_2 <- lus_spread %>% dplyr::group_by(part, lineupid, param_name) %>%
  dplyr::summarize(
    data_n = sum(true_model=="M2"),
    data_est = mean(M2[true_model=="M2"]),
    data_sd = sd(M2[true_model=="M2"], na.rm=TRUE),
    data_dist = data_est - max(M2[true_model=="M1"]),
    upper_qu = sum(data_est > M2[true_model=="M1"]) / (n()-1),
    data_panel = mean(panel_num[true_model=="M2"])
)

@@

<<>>=
jtts <- read.csv("Data/lineups-jtt.csv")
jtts$lineupid <- with(jtts, paste(model, m, rep, sep="-"))
jtts$data_panel <- jtts$plot_order
lus_summary_2 <- merge(lus_summary_2, jtts[, c("lineupid", "jtt", "data_panel")], by=c("lineupid","data_panel"), all.x=TRUE)
qplot(data=subset(lus_summary_2, param_name=="transitive triplets jumping alcohol2" & part=="smallfriends"), data_est, jtt, geom="jitter") + geom_label(data=subset(lus_summary_2, param_name=="transitive triplets jumping alcohol2" & jtt > 20 & part=="smallfriends"), aes(label=lineupid), alpha=.6)
@
